Warming Degrees and Flowering Trees

### 2025-04-03 paper/paper.qmd
Update paper.qmd
added some vizes and pickles

```{python}
with open("model/ols.pkl", "rb") as ols:
    model_0 = pickle.load(ols)

with open(model/ols_robust.pkl", "rb") as ols_robust:
    model_1 = pickle.load(ols_robust)
```

>>>>

```{python}
## Load the Pickled Models for faster visualizations
with open("../model/ols.pkl", "rb") as ols:
    model_0 = pickle.load(ols)

with open("../model/ols_robust.pkl", "rb") as ols_robust:
    model_1 = pickle.load(ols_robust)
```

```{python}
## Print nonrobust model summary
print(model_0.summary())
```

```{python}
## Print robust HC1 model summary
print(model_1.summary())
```

```{python}
## Visualizations
# Scatterplot with regression line
plt.figure(figsize=(10, 6))
sns.regplot(x='march_temp_c', y='flower_doy', data=df, ci=None, line_kws={'color': 'red'})
plt.text(0.1, 95, f"blooming_day = {model_0.params[1]:.2f} * temp + {model_0.params[0]:.2f}", color="red", fontsize=12)
plt.title("Sakura Blooming Day vs March Temperature")
plt.xlabel("March Avg Temperature (°C)")
plt.ylabel("Blooming Day of Year (DoY)")
plt.show()
```

```{python}
# Scatterplot with year-based color gradient
plt.figure(figsize=(10, 6))
scatter = plt.scatter(df['march_temp_c'], df['flower_doy'], c=df['year'], cmap='viridis', s=60, edgecolor='k')
plt.plot(X['march_temp_c'], model_0.predict(X), color='red', label='OLS Fit')
plt.text(-0.2, 95, f"blooming_day = {model_0.params[1]:.2f} * temp + {model_0.params[0]:.2f}", color="red", fontsize=12)
plt.colorbar(scatter, label='Year')
plt.title("Sakura Blooming DoY vs March Temperature with Year Gradient")
plt.xlabel("March Avg Temperature (°C)")
plt.ylabel("Blooming Day of Year (DoY)")
plt.legend()
plt.show()
```
